Racets: Embedding Policy{-}Agnostic Programming in Racket

### 2018-07-20 paper/paper.tex
the format of Sec3 semantics is fixed. Semantics should be all set now

\begin{figure*}
  \hfill \textit{(Metafunctions)}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
        \end{array}
      \end{displaymath}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
        \end{array}
      \end{displaymath}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {obs(\ell, b, bv)} & {=} & {bv} & & \\
          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
        \end{array}
      \end{displaymath}
\end{figure*}

>>>>

\begin{figure*}
  \hfill \textit{(Metafunctions)}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
        \end{array}
      \end{displaymath}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
        \end{array}
      \end{displaymath}
      \\
      \begin{displaymath}
        \begin{array}{rclrr}
          {obs(\ell, b, bv)} & {=} & {bv} & & \\
          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = & \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
        \end{array}
      \end{displaymath}
\end{figure*}
